---
author: Matthias Vogelgesang
title: Metropolis
subtitle: A modern beamer theme
institute: Center for modern beamer themes
date: \today
output: 
  binb::metropolis:
    citation_package: natbib
    includes:
      in_header: metropolis/header.tex
bibliography: metropolis/demo.bib
biblio-style: abbrvnat
toc: true
vignette: >
  %\VignetteIndexEntry{binb Metropolis Demo}
  %\VignetteKeywords{binb,vignette}
  %\VignettePackage{binb}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r,setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

# Introduction

## Metropolis

The \themename theme is a Beamer theme with minimal visual noise inspired
by the [hsrm](https://github.com/hsrmbeamertheme/hsrmbeamertheme) Beamer
Theme by Benjamin Weiss.

Enable the theme (in \LaTeX) by loading

```tex
\documentclass{beamer}
\usetheme{metropolis}
```

Note, that you have to have Mozilla's \emph{Fira Sans} font and XeTeX
installed to enjoy this wonderful typography.

\scriptsize In R you can of course use this package directly, see its documentation.

## Sections

Sections group slides of the same topic

```
## Elements
```

for which \themename provides a nice progress indicator \ldots


# Title formats

## Metropolis title formats

\themename supports 4 different title formats:

- Regular
- \textsc{Small caps}
- \textsc{all small caps}
- ALL CAPS

They can either be set at once for every title type or individually.


<!-- \metroset{titleformat frame=smallcaps} -->
<!-- ## Small caps -->

<!-- This frame uses the \texttt{smallcaps} title format. -->

<!-- \begin{alertblock}{Potential Problems} -->
<!-- Be aware that not every font supports small caps. If for example you -->
<!-- typeset your presentation with pdfTeX and the Computer Modern Sans Serif -->
<!-- font, every text in small caps will be typeset with the Computer Modern -->
<!-- Serif font instead.  -->
<!-- \end{alertblock} -->




<!-- \metroset{titleformat frame=allsmallcaps} -->
<!-- ## All small caps -->

<!-- This frame uses the \texttt{allsmallcaps} title format. -->

<!-- \begin{alertblock}{Potential problems} -->
<!-- As this title format also uses small caps you face the same problems as -->
<!-- with the \texttt{smallcaps} title format. Additionally this format can -->
<!-- cause some other problems. Please refer to the documentation if you -->
<!-- consider using it. -->

<!-- As a rule of thumb: just use it for plaintext-only titles. -->
<!-- \end{alertblock} -->


# Elements

## Typography

```
The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.
```

\begin{center}becomes\end{center}

The theme provides sensible defaults to \emph{emphasize} text,
\alert{accent} parts or show \textbf{bold} results.


## Font feature test

- Regular
- \textit{Italic} (also _Italic_)
- \textsc{Small Caps}
- \textbf{Bold} (also **Bold**)
- \textbf{\textit{Bold Italic}} (also **_Italic_**)
- \textbf{\textsc{Bold Small Caps}}
- \texttt{Monospace}
- \texttt{\textit{Monospace Italic}}
- \texttt{\textbf{Monospace Bold}}
- \texttt{\textbf{\textit{Monospace Bold Italic}}}


## Lists
\begin{columns}[T,onlytextwidth]
  \column{0.33\textwidth}
    Items
    \begin{itemize}
      \item Milk \item Eggs \item Potatoes
    \end{itemize}

  \column{0.33\textwidth}
    Enumerations
    \begin{enumerate}
      \item First, \item Second and \item Last.
    \end{enumerate}

  \column{0.33\textwidth}
    Descriptions
    \begin{description}
      \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
    \end{description}
\end{columns}


## Animation (using \LaTeX\ )

\begin{itemize}[<+- | alert@+>]
  \item \alert<4>{This is\only<4>{ really} important}
  \item Now this
  \item And now this
\end{itemize}

\bigskip
\scriptsize This uses \LaTeX\ for aninmation. The next slides uses RMarkdown

## Animation (using RMarkdown, plus one \LaTeX\ trick)

::: incremental 

- \alert<4>{This is\only<4>{ really} important}
- Now this
- And now this

:::



## Figures (using \LaTeX)

\begin{figure}
  \newcounter{density}
  \setcounter{density}{20}
  \begin{tikzpicture}
    \def\couleur{alerted text.fg}
    \path[coordinate] (0,0)  coordinate(A)
                ++( 90:5cm) coordinate(B)
                ++(0:5cm) coordinate(C)
                ++(-90:5cm) coordinate(D);
    \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
    \foreach \x in {1,...,40}{%
        \pgfmathsetcounter{density}{\thedensity+20}
        \setcounter{density}{\thedensity}
        \path[coordinate] coordinate(X) at (A){};
        \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
                            -- (C) coordinate[pos=.10](B)
                            -- (D) coordinate[pos=.10](C)
                            -- (X) coordinate[pos=.10](D);
        \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
    }
  \end{tikzpicture}
  \caption{Rotated square from
  \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
\end{figure}

\scriptsize This used a \LaTeX\ feature. All RMarkdown features are also at our disposal.


## Tables (using \LaTeX})

\begin{table}
  \caption{Largest cities in the world (source: Wikipedia)}
  \begin{tabular}{@{} lr @{}}
    \toprule
    City & Population\\
    \midrule
    Mexico City & 20,116,842\\
    Shanghai & 19,210,000\\
    Peking & 15,796,450\\
    Istanbul & 14,160,467\\
    \bottomrule
  \end{tabular}
\end{table}

\scriptsize This used a \LaTeX\ feature. All RMarkdown features are also at our disposal.


## Blocks

Three different block environments are pre-defined and may be styled with an
optional background color.

\begin{columns}[T,onlytextwidth]
  \column{0.5\textwidth}
    \begin{block}{Default}
      Block content.
    \end{block}

    \begin{alertblock}{Alert}
      Block content.
    \end{alertblock}

    \begin{exampleblock}{Example}
      Block content.
    \end{exampleblock}

  \column{0.5\textwidth}

     \metroset{block=fill}

    \begin{block}{Default}
      Block content.
    \end{block}

    \begin{alertblock}{Alert}
      Block content.
    \end{alertblock}

    \begin{exampleblock}{Example}
      Block content.
    \end{exampleblock}

\end{columns}

\bigskip

\scriptsize The right side uses the `\metroset{block=fill}` option. Blocks
can also used in Markdown using `###` (if slide-level=2).


## Math

\begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
\end{equation*}

## Line plots

\begin{figure}
  \begin{tikzpicture}
    \begin{axis}[
      mlineplot,
      width=0.9\textwidth,
      height=6cm,
    ]

      \addplot {sin(deg(x))};
      \addplot+[samples=100] {sin(deg(2*x))};

    \end{axis}
  \end{tikzpicture}
\end{figure}


## Bar charts

\begin{figure}
  \begin{tikzpicture}
    \begin{axis}[
      mbarplot,
      xlabel={Foo},
      ylabel={Bar},
      width=0.9\textwidth,
      height=6cm,
    ]

    \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
    \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
    \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};

    \legend{lorem, ipsum, dolor}

    \end{axis}
  \end{tikzpicture}
\end{figure}


## Quotes

> Veni, Vidi, Vici

## References

Some references \citep{knuth92,ConcreteMath,Simpson,Er01,greenwade93}

\bigskip

\scriptsize `allowframebreaks` is not used or needed, also changed `\cite` to
`\citep`, and defaulted `natbib` to option `[round]`.

# Conclusion

## Summary

Get the source of this theme and the demo presentation from

\begin{center}\url{https://github.com/matze/mtheme}\end{center}

The theme \emph{itself} is licensed under a [Creative Commons
Attribution-ShareAlike 4.0 International
License](http://creativecommons.org/licenses/by-sa/4.0/)

\begin{center}\ccbysa\end{center}

\scriptsize Source and documentation for the RMarkdown variant are at \url{https://github.com/eddelbuettel/binb}.

_ _ _

Questions?




## Backup slides

Sometimes, it is useful to add slides at the end of your presentation to
refer to during audience questions.

The best way to do this is to include the `appendixnumberbeamer`
package in your preamble and call `\appendix` before your backup slides.

\themename will automatically turn off slide numbering and progress bars for
slides in the appendix.

\scriptsize Calling `\appendix` currently leads to an error in when using `binb`.

## R Appendix: R Figure Example

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):

```{r pressureCode, eval=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Appendix: R Figure Example
  
```{r pressureFig, echo=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Appendix: R Table Example
  
A simple `knitr::kable` example:  

```{r kableEx}
knitr::kable(mtcars[1:5, 1:8],
             caption="(Parts of) the mtcars dataset")
```

