---
author: Rahul Saha
address: www.ratulsaha.com
title: PRESENTO
subtitle: clean, simple and extensible
date: \today
output: binb::presento
---


## Presento

- \begin{center}\largetext{The design is \underline{clean}}\end{center}    \bigskip
- \begin{center}\largetext{The rules are \underline{simple}}\end{center}   \bigskip
- \begin{center}\largetext{The code is \underline{extensible}}\end{center}

## Open Source Fonts

-  \montserratfont This is \textsc{Montserrat}	\bigskip
-  \notosansfont This is \textsc{Noto Sans}		\bigskip
-  \latolightfont This is Lato (light)          \bigskip
-  \inconsolatafont This is inconsolata         \bigskip
-  \textsc{This is Alegreya Sans small caps}    \bigskip

## Color Palette

\begin{center}
  \crule[colordgray] \crule[colorhgray] \crule[colorblue] \crule[colorgreen] \crule[colororange]
\end{center}

____

\begin{center}
 \hugetext{BIG BOLD TEXT} 
 \medskip 
 \small but background color does not work
\end{center}


____

\tikz[overlay,remember picture] \node[opacity=0.8, at=(current page.center)]{%
  \includegraphics[width=\paperwidth]{images/skeleton}};
\begin{textblock}{7}(7,2.5)
  {\color{colorblue}\hugetext{\textbf{RUN!}}}
\end{textblock}




## R Appendix: R Figure Example

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):

\small

```{r pressureCode, eval=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Appendix: R Figure Example
  
```{r pressureFig, echo=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```  

## R Appendix: R Table Example
  
A simple data example:  

```{r notkableEx}
mtcars[1:5, 1:5]
```

